ICT and Future Productivity:\\Evidence and Theory of a GPT\thanks{Correspondence: Department of Economics, Boston College, 140 Commonwealth Avenue, Chestnut Hill, MA 02467. Email: brianti@bc.edu (Marco Brianti) and gati@bc.edu (Laura G\'ati).}

### 2018-07-31 Latex/Draft_Summer2018/Summer2018.tex
final changes agreed together

\
%%%%%%%%%%%%%%%%%%%%             ABSTRACT           %%%%%%%%%%%%%%%%%% 
\small{
\abstract{We employ Structural VARs to investigate the effects of ICT supply shocks on Total Factor Productivity (TFP) and other macroeconomic variables. In response to this sector-specific supply shock, relative prices of ICT goods and services immediately fall, ICT investment rises on impact, and TFP displays a significant delayed and persistent increase. Taking up the view of theories of ICT as a general-purpose technology, we analyze a two-sector general equilibrium model in order to rationalize previous results and estimate spillovers from the stock of ICT via impulse-response matching. We conclude that ICT accumulation is able to enhance productivity through a positive spillover effect which takes into account the overall level of diffusion of ICT capital in the economy.}
}
\newpage

@@

Along with \cite{comin2006medium}, theoretical contributions rationalize endogenous productivity dynamics by incorporating features of endogenous growth models in standard models of business cycles. Following \cite{romer1990endogenous}, most of these papers augment final-good production functions with an expanding composite of intermediate goods invented by the Research \& Development (R\&D) sector in order to allow for an endogenous rate of adoption of new technologies.\footnote{\cite{bianchi2014growth}, \cite{anzoategui2016endogenous}, and \cite{moran2017innovation} use similar techniques to endogenize growth. \cite{bianchi2014growth} augment a DSGE  model using a quality ladders model in the vein of \cite{grossman1991quality}. \cite{anzoategui2016endogenous} and \cite{moran2017innovation}, similarly to \cite{comin2006medium}, use a model of expanding variety \`a la \cite{romer1990endogenous}.} Guided by the prediction of such theoretical work that R\&D developments matter for growth, other papers attempt to provide empirical evidence of a slowdown in the productivity of the R\&D sector. Specifically, they show that although research effort keeps rising, the rate of new ideas and discoveries is slowing down.\footnote{\cite{jones2009burden} and \cite{bloom2017ideas} are two contributions that highlight these facts.}

@@

We use two identifying restrictions in order to back out an ICT technology shock. First, we expect it to be orthogonal to the current productivity of all the other sectors. Since the share of the ICT sector accounts for a negligible part of the whole economy, ICT shocks should have an approximately zero effect on TFP on impact. Thus, our first restriction will be a zero-impact restriction on TFP after an ICT shock. Moreover, following \cite{greenwood1997long} and \cite{fisher2006dynamic}, we rely on RP and ICTI because we expect that a sectoral technology shock should decrease the relative prices of the sector while enhancing expenditure in the underlying sector. For theoretical reasons discussed in more detail below, we do not impose any restriction on RP; instead, we let the ICT shock maximize the impact response of ICTI.\footnote{As pointed out by both \cite{greenwood2000role} and \cite{basu2010sector}, letting the the direction of RP be the sole identifying restriction does not properly capture technological changes between sectors. This is the main reason why we do not impose the direction of RP as a direct identifying condition. While our main robustness check uses RP, also there we refrain from considering the direction of the RP response. See Section \ref{section:twosteps}.} In response to this shock, ICTI rises on impact and remains significant for several quarters. RP persistently and significantly declines for more than two years, suggesting that we are indeed identifying the correct sectoral shock. Our main result is that TFP, restricted not to respond on impact, rises after few quarters and remains significant and stable for at least 5 years, despite the tiny size of the ICT sector relative to the economy. Finally, variance decomposition analysis suggests that ICT shocks explain a remarkable size of economic fluctuations over the medium and long run. These shocks drive about $40$\% and $33$\% of the overall GDP and TFP fluctuations over a 10-year horizon, respectively.

@@

Using a notation similar to \cite{barsky2011news}, we implement our identification strategy as follows. Let $y_t$ be the $(5 \times 1)$ vector of observables of length $T$ presented above. The reduced-form VAR takes the following form,
$$
y_t = B(L)y_{t-1} + i_t 
$$
Assume now that there exists a linear combination that maps innovations $i_t$ to structural shocks $s_t$,
$$
A_0 s_t = i_t
$$
which implies the structural-form VAR
$$
A_0^{-1}y_t = C(L) y_{t-1} + s_t
$$
where $C(L) = A_0^{-1} B(L)$ and $s_t = A_0^{-1} i_t$. The impact matrix $A_0$ must be such that $\Sigma = A_0 A_0'$. Notice that $A_0$ is not unique since for any $D$ such that $DD' = I$, $\tilde{A}_0 = A_0 D$ satisfies $\Sigma = \tilde{A}_0 \tilde{A}_0'$.

The matrix of impact responses to all shocks is: % TYPO HERE? either Atilde or A0 D. Checked Barsky, this seems correct but I'm confused. 
$$
\Pi(0) = \tilde{A}_0 D
$$
and is specifically formed by the following elements, denoting the responses of variable $i$ to shock $j$, % same here
$$
\Pi_{i,j}(0) = e_i' \tilde{A}_0 D e_j
$$
where $e_k$ is a selector column vector of the same dimension as $\tilde{A}_0$ with $1$ in the $k$th element and zero elsewhere. In particular, notice that $e_j$ is selecting a specific column of $D$. Let this column be denoted by $\gamma_j$. Using this notation, $\tilde{A}_0\gamma_j$ is the vector of impact responses of all the variable to shock $j$.

@@

Secondly, a long line of literature going back to the early 1990s postulates that ICT may be a general-purpose technology.\footnote{\cite{basu2003case}, \cite{basu2007information} and \cite{oliner2000resurgence} and are some examples.} % need to include Brynjolfsson's work here, the all-star paper and the Gordon-Mokyr debate.
Following the classical definition of BT,
% Bresnahan Trajtenberg -- need to get citation right
 GPTs are technologies that alter the process of economy-wide production, and thus affect the productivity of the entire economy. This effect can come about  through several channels. For example, investment in ICT goods may trigger accumulation of unobserved complementary capital, as suggested by both \cite{basu2003case} and \cite{basu2007information}. Conversely, as advocated by Brynjolffson, new ICT goods may change managerial practices, thus affecting the production process. We take a broader view in which we simply consider the diffusion of ICT goods to be the crucial element of ICT's general-purpose nature.

@@

The production side of the final-good sector consists of a set $[0,1]$ of firms. In each period, final-good firm $j \in [0,1]$ produces $y^c_t(j)$ using the services of labor $l_{t}$, and two types of capital: hard capital, $k^c_{t}$ and ICT capital, $k^i_{t}$. In addition, the production function is augmented with (i) neutral productivity common across sectors, (ii) sector-specific productivity, and (iii) a positive spillover effect related to the diffusion of ICT capital in the whole economy. Production of final output of firm $j$ is undertaken in accordance with
\begin{eqnarray}\label{equation:production_FINAL}
y^c_t(j) = A^c_t \ \big( k^c_{t}(j) \big)^a \ \big( k^i_{t}(j) \big)^b \ \big( l_{t}(j) \big)^{1-a-b}, \ \ 0 < a,b < 1
\end{eqnarray}
where productivity is equal to $ A_t^c = \eta_t \ \theta^c_t \ (k^i_{t})^{\gamma} $. $\eta_t$ is the neutral technological component which moves along the following deterministic trend
\begin{eqnarray}\label{equation:neutral_tech_process}
\eta_t = (\Gamma^{\eta})^t e^{\varepsilon_t},  
\end{eqnarray} 
\begin{eqnarray}\label{equation:neutral_tech_shock}
 \varepsilon_t = \rho_{\nu} \varepsilon_{t-1} + \nu_t
\end{eqnarray} 
where $\rho_{\nu} \in (0,1)$ and $\nu_t \sim N(0,\sigma_{\nu}^2)$ represents a neutral technology shock. $\theta^c_t$ is the sector-specific technological component,  which moves along the following deterministic trend
\begin{eqnarray}
\theta_t^c = (\Gamma^{c})^t.
\end{eqnarray} 
Then, $\gamma$ represents the parameter that governs the size of the spillover effect of ICT capital in the production function. Moreover, $k^c_{t}(j)$ is the part of hard capital $k^c_t$ used by firm $j$ in oder to produce final-good output. Similarly, $k^i_{t}(j)$ and $l_{t}(j)$ are the parts of ICT capital $k^i_t$ and labor $l_t$ used by firm $j$ in oder to produce final-good output, respectively.

@@

Production of ICT capital goods is symmetric to final-output production. It is populated by a set $[0,1]$ of firms. Similarly, ICT-good firm $q \in [0,1]$ produces $y^i_t(q)$ with labor $l_{t}$, hard capital, $k^c_{t}$ and ICT capital, $k^i_{t}$. Analogously to the first sector, production function is augmented by neutral productivity $\eta_t$, sector-specific productivity $\theta^i_t$, and the spillover effect $(k^i_{t})^{\gamma}$. Firm $q$ produces in accordance with
\begin{eqnarray}\label{equation:productionICT}
y^i_t(q) = \eta_t \ \theta^i_t \ (k^i_{t})^{\gamma} \ \ \big( k^c_{t}(q) \big)^a \ \big( k^i_{t}(q) \big)^b \ \big( l_{t}(q) \big)^{1-a-b}, \ \ 0 < a,b < 1
\end{eqnarray}
where $\theta^i_t$ is the sector-specific technological component which moves along the following deterministic trend
\begin{eqnarray}\label{equation:ICT_tech_process}
\theta^i_t = (\Gamma^{i})^t e^{\zeta_t},  
\end{eqnarray} 
\begin{eqnarray}\label{equation:ICT_tech_shock}
\zeta_t = \rho_{\iota} \zeta_{t-1} + \iota_t
\end{eqnarray} 
where $\rho_{\iota} \in (0,1)$ and $\iota_t \sim N(0,\sigma_{\iota}^2)$ represents an ICT technology shock. In line with the first sector, $k^c_{t}(q)$ is the part of hard capital $k^c_t$ used by firm $q$ in oder to produce ICT goods. Similarly, $k^i_{t}(q)$ and $l_{t}(q)$ are the parts of ICT capital $k^i_t$ and labor $l_t$ used by firm $q$ in oder to produce ICT goods, respectively.

@@

We calibrate the model at a quarterly frequency. We set the discount factor $\beta$ to $0.97^{\frac{1}{4}}$ to match the average yield of $3$\% of the 3-month Treasury bill using data from 1989:Q1 to 2017:Q1. We set the ICT share $b$ equal to $0.0310$ following \cite{oulton2012long} and hard capital share $a$ equal to $0.3$. Moreover, adapting \cite{oulton2012long} accordingly to our additional assumptions, we derive steady state growth rates of final-sector technology $\Gamma^c$ and ICT-sector technology $\Gamma^i$ from solving the system,
\begin{equation}\label{equation:system_param}
\begin{cases}
 \frac{p_t}{p_{t-1}}  = \frac{\Gamma^c}{\Gamma^i} \\
 \frac{c_t}{c_{t-1}}  = (\Gamma^c)^{\frac{1-b-\gamma}{1-a-b-\gamma}}  (\Gamma^i)^{\frac{b+\gamma}{1-a-b-\gamma}}
\end{cases}
\end{equation}
where $p_t/p_{t-1}$ and $c_t/c_{t-1}$ are derived from the simple mean of their empirical related values using quarterly data from 1989:Q1 to 2017:Q1. This implies $\Gamma^c = 1.0034$ and $\Gamma^i = 1.0160$.\footnote{Notice that the value of $\gamma$ is unknown at this step since it is going to be evaluated using impulse-response matching. This implies that the solution for $\Gamma^c$, $\Gamma^i$, and $\gamma$ should be a fixed point where given $\gamma^*$ we obtain $(\Gamma^i)^*$ and $(\Gamma^c)^*$ solving \ref{equation:system_param}. Given $(\Gamma^i)^*$ and $(\Gamma^c)^*$ we obtain $\gamma^*$ by minimizing the impulse-response matching. At this step, however, we are simply solving the system assuming $\gamma$ equal to zero, but a more refined solution will be provided in future.} Finally, to avoid an over-identification problem we set the growth rate of sector-neutral technology $\Gamma^{\eta}$ equal to one.

@@

Table \ref{table:estimated_parameters} in Appendix \ref{sec:appendix_table_IRmatching} shows results of Problem \ref{equation:min_prob_IRmatching}. The estimate of the spillover effect of ICT capital on TFP, $\gamma$, is $0.58$, while estimates of variance and persistence of an ICT-specific technological shock $\sigma^2_{\iota}$ and $\rho_{\iota}$ are $0.01$ and $0.9$ respectively.\footnote{Estimated parameter values are strongly robust to various alternative specifications. Using different empirical results, changing the initial calibration, the number of parameters matched or the methodology do not qualitative change the estimated value of $\gamma$ close to $0.6$.} These results convey a number of interesting messages regarding the fit of our two-sector model. Most importantly, the key question of our model was whether the presence of ICT shocks alone can account for the empirical responses we observe in data, or whether ICT diffusion plays a crucial role in this dynamics. This amounts to asking whether $\gamma = 0$ is supported by the data. Clearly, our estimate of $0.58$ rejects this hypothesis strongly. Thus, the data favor an interpretation of our model in which there are considerable spillovers to ICT capital. Accordingly, ICT shocks do not need to be large in magnitude to have sizable effects on TFP, GDP and consumption. This is indicated by the relatively small number we obtain for $\sigma^2_{\iota}$ of $0.01$. Confronted with data, the model is clearly telling a story in which there are small, but persistent ($\rho_{\iota} = 0.9$) ICT shocks that lead considerable medium-run TFP growth because of large spillovers from ICT capital accumulation.
% does it make sense? I dont know what to say for sigmaiota and rhoiota...

>>>>

\
%%%%%%%%%%%%%%%%%%%%             ABSTRACT           %%%%%%%%%%%%%%%%%% 
\small{
\abstract{We employ Structural VARs to investigate the effects of technological shocks specific to the ICT sector on Total Factor Productivity (TFP) and other macroeconomic variables. In response to this sector-specific technological change, relative prices of ICT goods and services immediately fall, ICT investment rises on impact, and TFP displays a significant delayed and persistent increase. Moreover, current ICT supply shocks explain almost one third of overall TFP fluctuations over a 10-year horizon. Taking up the view of theories of ICT as a general-purpose technology, we analyze a two-sector general equilibrium model in order to rationalize previous results and estimate spillovers from the stock of ICT via impulse-response matching. We conclude that ICT accumulation is able to enhance productivity through a positive spillover effect which takes into account the overall level of diffusion of ICT capital in the economy.}
}
\newpage

@@

Along with \cite{comin2006medium}, theoretical contributions rationalize endogenous productivity dynamics by incorporating features of endogenous growth models in standard models of business cycles. Following \cite{romer1990endogenous}, most of these papers augment final-good production functions with an expanding composite of intermediate goods invented by the Research \& Development (R\&D) sector in order to allow for an endogenous rate of adoption of new technologies.\footnote{\cite{bianchi2014growth}, \cite{anzoategui2016endogenous}, \cite{moran2017innovation} and \cite{guerron2015financial} use similar techniques to endogenize growth. \cite{bianchi2014growth} augment a DSGE  model using a quality ladders model in the vein of \cite{grossman1991quality}. \cite{anzoategui2016endogenous}, \cite{moran2017innovation} and \cite{guerron2015financial}, similarly to \cite{comin2006medium}, use a model of expanding variety \`a la \cite{romer1990endogenous}.} Guided by the prediction of such theoretical work that R\&D developments matter for growth, other papers attempt to provide empirical evidence of a slowdown in the productivity of the R\&D sector. Specifically, they show that although research effort keeps rising, the rate of new ideas and discoveries is slowing down.\footnote{\cite{jones2009burden} and \cite{bloom2017ideas} are two contributions that highlight these facts.}

@@

We use two main identifying restrictions in order to back out an ICT technology shock: (i) it must be orthogonal to current total factor productivity and (ii) maximize the impact effect on ICT investment. First of all, Restriction (i) is justified because the share of the ICT sector accounts for a negligible part of the whole economy implying that ICT shocks should have approximately zero impact effect on TFP. In other words, although TFP embodies ICT technical changes by construction, we argue that the direct impact effect of an ICT technological shock on TFP is so tiny to be approximately neglected in our identifying restriction. Moreover, we follow results by \cite{greenwood1997long} and \cite{fisher2006dynamic} (among others) to support Restriction (ii). In particular, a vast body of literature on sector-specific technological changes argues that a sectoral technology shock should boost quantities in the underlying sector implying a current large impact effect on ICT investment.\footnote{For theoretical reasons discussed in more detail in Section \ref{section:empirics}, we do not impose any restriction on RP in our main specification; instead, we let the ICT shock maximize the impact response of ICTI. As pointed out by both \cite{greenwood2000role} and \cite{basu2010sector}, letting the the direction of RP be the sole identifying restriction does not properly capture technological changes between sectors. This is the main reason why we do not impose the direction of RP as a direct identifying condition.}

In response to this shock, ICTI rises on impact and remains significant for several quarters. RP persistently and significantly declines for more than two years, suggesting that we are indeed identifying the correct sectoral shock. Our main result is that TFP, restricted not to respond on impact, rises after few quarters and remains significant and stable for at least 5 years, despite the tiny size of the ICT sector relative to the economy. Finally, variance decomposition analysis suggests that ICT shocks explain a remarkable size of economic fluctuations over the medium and long run. These shocks drive about $40$\% and $33$\% of the overall GDP and TFP fluctuations over a 10-year horizon, respectively.

@@

Using a notation similar to \cite{barsky2011news}, we implement our identification strategy as follows. Let $y_t$ be the $(5 \times 1)$ vector of observables of length $T$ presented above. The reduced-form VAR takes the following form,
$$
y_t = B(L)y_{t-1} + i_t 
$$
Assume now that there exists a linear combination that maps innovations $i_t$ to structural shocks $s_t$,
$$
A_0 s_t = i_t
$$
which implies the structural-form VAR
$$
A_0^{-1}y_t = C(L) y_{t-1} + s_t
$$
where $C(L) = A_0^{-1} B(L)$ and $s_t = A_0^{-1} i_t$. The impact matrix $A_0$ must be such that $\Sigma = A_0 A_0'$. Notice that for any arbitrary orthogonalization $\tilde{A}_0$ such that $\Sigma = \tilde{A}_0 \tilde{A}_0'$, impact matrix $A_0$ can be back out by the appropriate orthonormal matrix $D$ ($DD' = I$) where $A_0 = \tilde{A}_0 D$.

Thus, the matrix of impact responses to all shocks is: % TYPO HERE? either Atilde or A0 D. Checked Barsky, this seems correct but I'm confused. 
$$
\Pi(0) = \tilde{A}_0 D
$$
and is specifically formed by the following elements, denoting the responses of variable $i$ to shock $j$, % same here
$$
\Pi_{i,j}(0) = e_i' \tilde{A}_0 D e_j
$$
where $e_k$ is a selector column vector of the same dimension as $\tilde{A}_0$ with $1$ in the $k$th element and zero elsewhere. In particular, notice that $e_j$ is selecting a specific column of $D$. Let this column be denoted by $\gamma_j$. Using this notation, $\tilde{A}_0\gamma_j$ is the vector of impact responses of all the variable to shock $j$.

@@

Secondly, a long line of literature going back to the early 1990s postulates that ICT may be a general-purpose technology.\footnote{\cite{oliner2000resurgence}, \cite{basu2003case}, and \cite{basu2007information} are some examples. In addition, we are somehow related to the so-called Gordon-Mokyr debate where the two authors present opposing views of future innovation. Among the series of published papers we highlight the followings two: \cite{gordon2012us} and \cite{mokyr2014secular}.}

Following the classical definition of \cite{bresnahan1992general},
 GPTs are technologies that alter the process of economy-wide production, and thus affect the productivity of the entire economy. This effect can come about  through several channels. For example, investment in ICT goods may trigger accumulation of unobserved complementary capital, as suggested by both \cite{basu2003case} and \cite{basu2007information}. Conversely, as advocated by \cite{bresnahan2002information}, new ICT goods may change managerial practices, thus affecting the production process. We take a broader view in which we simply consider the diffusion of ICT goods to be the crucial element of ICT's general-purpose nature.

@@

The production side of the final-good sector consists of a set $[0,1]$ of firms. In each period, final-good firm $j \in [0,1]$ produces $y^c_t(j)$ using the services of labor $l_{t}$, and two types of capital: hard capital, $k^c_{t}$ and ICT capital, $k^i_{t}$. In addition, the production function is augmented with (i) neutral productivity common across sectors, (ii) sector-specific productivity, and (iii) a positive spillover effect related to the diffusion of ICT capital in the whole economy. Production of final output of firm $j$ is undertaken in accordance with
\begin{eqnarray}\label{equation:production_FINAL}
y^c_t(j) = A^c_t \ \big( k^c_{t}(j) \big)^a \ \big( k^i_{t}(j) \big)^b \ \big( l_{t}(j) \big)^{1-a-b}, \ \ 0 < a,b < 1
\end{eqnarray}
where productivity is equal to $ A_t^c = \eta_t \ \theta^c_t \ (k^i_{t})^{\gamma} $. $\eta_t$ is the neutral technological component which moves along the following deterministic trend
\begin{eqnarray}\label{equation:neutral_tech_process}
\eta_t = (\Gamma^{\eta})^t e^{\varepsilon_t},  
\end{eqnarray} 
\begin{eqnarray}\label{equation:neutral_tech_shock}
 \varepsilon_t = \rho_{\nu} \varepsilon_{t-1} + \nu_t
\end{eqnarray} 
where $\rho_{\nu} \in (0,1)$ and $\nu_t \sim N(0,\sigma_{\nu}^2)$ represents a neutral technology shock.\footnote{In this case, a news shock would be a current signal regarding innovations to the future values of $\eta_t$.} $\theta^c_t$ is the sector-specific technological component,  which moves along the following deterministic trend
\begin{eqnarray}
\theta_t^c = (\Gamma^{c})^t.
\end{eqnarray} 
Then, $\gamma$ represents the parameter that governs the size of the spillover effect of ICT capital in the production function. Moreover, $k^c_{t}(j)$ is the part of hard capital $k^c_t$ used by firm $j$ in oder to produce final-good output. Similarly, $k^i_{t}(j)$ and $l_{t}(j)$ are the parts of ICT capital $k^i_t$ and labor $l_t$ used by firm $j$ in oder to produce final-good output, respectively.

@@

Production of ICT capital goods is symmetric to final-output production. It is populated by a set $[0,1]$ of firms. Similarly, ICT-good firm $q \in [0,1]$ produces $y^i_t(q)$ with labor $l_{t}$, hard capital, $k^c_{t}$ and ICT capital, $k^i_{t}$. Firm $q$ produces in accordance with
\begin{eqnarray}\label{equation:productionICT}
y^i_t(q) = A_t^i \ \big( k^c_{t}(q) \big)^a \ \big( k^i_{t}(q) \big)^b \ \big( l_{t}(q) \big)^{1-a-b}, \ \ 0 < a,b < 1
\end{eqnarray}
where  $A_t^i = \eta_t \ \theta^i_t \ (k^i_{t})^{\gamma}$. Analogously to the first sector, production function is augmented by neutral productivity $\eta_t$, sector-specific productivity $\theta^i_t$, and the spillover effect $(k^i_{t})^{\gamma}$. In particular, $\theta^i_t$ is the sector-specific technological component which moves along the following deterministic trend
\begin{eqnarray}\label{equation:ICT_tech_process}
\theta^i_t = (\Gamma^{i})^t e^{\zeta_t},  
\end{eqnarray} 
\begin{eqnarray}\label{equation:ICT_tech_shock}
\zeta_t = \rho_{\iota} \zeta_{t-1} + \iota_t
\end{eqnarray} 
where $\rho_{\iota} \in (0,1)$ and $\iota_t \sim N(0,\sigma_{\iota}^2)$ represents an ICT technology shock. In line with the first sector, $k^c_{t}(q)$ is the part of hard capital $k^c_t$ used by firm $q$ in oder to produce ICT goods. Similarly, $k^i_{t}(q)$ and $l_{t}(q)$ are the parts of ICT capital $k^i_t$ and labor $l_t$ used by firm $q$ in oder to produce ICT goods, respectively.

@@

We calibrate the model at a quarterly frequency. We set the discount factor $\beta$ to $0.97^{\frac{1}{4}}$ to match the average yield of $3$\% of the 3-month Treasury bill using data from 1989:Q1 to 2017:Q1. We set the ICT share $b$ equal to $0.0310$ following \cite{oulton2012long} and hard capital share $a$ equal to $0.3$. Moreover, adapting \cite{oulton2012long} accordingly to our additional assumptions, we derive steady state growth rates of final-sector technology $\Gamma^c$ and ICT-sector technology $\Gamma^i$ from solving the system,
\begin{equation}\label{equation:system_param}
\begin{cases}
 \frac{p_t}{p_{t-1}}  = \frac{\Gamma^c}{\Gamma^i} \\
 \frac{c_t}{c_{t-1}}  = (\Gamma^c)^{\frac{1-b-\gamma}{1-a-b-\gamma}}  (\Gamma^i)^{\frac{b+\gamma}{1-a-b-\gamma}}
\end{cases}
\end{equation}
where $p_t/p_{t-1}$ and $c_t/c_{t-1}$ are derived from the simple mean of their empirical related values using quarterly data from 1989:Q1 to 2017:Q1. This implies $\Gamma^c = 1.0034$ and $\Gamma^i = 1.0160$.\footnote{Notice that the value of $\gamma$ is unknown at this step since it is going to be evaluated using impulse-response matching. This implies that the solution for $\Gamma^c$, $\Gamma^i$, and $\gamma$ should be a fixed point where given $\gamma^*$ we obtain $(\Gamma^i)^*$ and $(\Gamma^c)^*$ solving \ref{equation:system_param}. Given $(\Gamma^i)^*$ and $(\Gamma^c)^*$ we obtain $\gamma^*$ by minimizing the impulse-response matching. At this step, however, we are simply solving the system assuming $\gamma$ equal to zero, but a more refined solution will be provided in future.}\footnote{Other different systems might be use in order to pin down the steady state growth rates of both sectors. At this first stage, we opt for System \ref{equation:system_param} because both relative prices and aggregate consumption are well observable variables in the data.} Finally, to avoid an over-identification problem we set the growth rate of sector-neutral technology $\Gamma^{\eta}$ equal to one.

@@

Table \ref{table:estimated_parameters} in Appendix \ref{sec:appendix_table_IRmatching} shows results of Problem \ref{equation:min_prob_IRmatching}. The estimate of the spillover effect of ICT capital on TFP, $\gamma$, is $0.58$, while estimates of variance and persistence of an ICT-specific technological shock $\sigma^2_{\iota}$ and $\rho_{\iota}$ are $0.01$ and $0.9$ respectively.\footnote{Estimated parameter values are strongly robust to various alternative specifications. Using different empirical results, changing the initial calibration, the number of parameters matched or the methodology do not qualitative change the estimated value of $\gamma$ close to $0.6$.} These results convey a number of interesting messages regarding the fit of our two-sector model. Most importantly, the key question of our model was whether the presence of ICT shocks alone can account for the empirical responses we observe in data, or whether ICT diffusion plays a crucial role in this dynamics. This amounts to asking whether $\gamma = 0$ is supported by the data. Clearly, our estimate of $0.58$ rejects this hypothesis strongly. Thus, the data favor an interpretation of our model in which there are considerable spillovers to ICT capital. Accordingly, ICT shocks do not need to be extremely large in magnitude to have sizable effects on TFP, GDP and consumption. This is indicated by the value we obtain for $\sigma^2_{\iota}$ of $0.01$. Confronted with data, the model is clearly telling a story in which there are small (relative to the overall economy) but persistent ($\rho_{\iota} = 0.9$) ICT shocks that lead considerable medium-run effect on TFP and consumption because of large spillovers from ICT capital accumulation.
